State and Input Dependent Disturbances in Min-Max Model Predictive Control

### 2016-07-17 draft.tex
Modified for ellipsoids.
what happened

[ticket: X]

%% Ticket list
\openTickets{Manuel:convHull,Manuel:wlog,Manuel:invertability:assumption,Mark:log:bounds,Mark:proof:cor15,Manuel:proof:rewritten}

@@

In this section we define the property of \emph{parametric convexity} in the context of set valued maps (so called point-to-set maps, see e.g.~\cite{Hogan:1973}). This property is then used 
%here and in Section~\ref{sec:example:I} 
to demonstrate the convexity of a generalised Pontryagin difference and thus determine the conditions under which $\mathcal{X}^\infty$ and $\mathcal{X}_i$ are convex polyhedra. 
In this section we refer to sets $Y\subseteq\mathbb R^d$ and $Z\subseteq\mathbb R^n$, and we denote the power set of $Z$ as $\mathscr P(Z)$.

@@

Notice that Definition~\ref{def:parametric:convexity} does not require convexity of~$\mathcal W(p)$. However, we will only consider maps~$\mathcal W$ for which $\mathcal W(p)$ is convex for all fixed $p\in Y$.

\subsection{Properties of Parametrically Convex Maps}\label{ssec:properties:of:p:convex:maps}
%
We begin by introducing an equivalent characterisation of parametric convexity that provides an insight into the geometrical properties of 
point-to-set maps satisfying~(\ref{eq:def:parametrically:convex}).
%Definition~\ref{def:parametric:convexity}. 
This is based on a description of parametric convexity in terms of conditions on the graph of a point-to-set map.
%
\begin{defi}\label{def:graph:of:map}
Let $\mathcal W:Y\rightarrow \mathscr P(Z)$ be a continuous point-to-set map
such that $\mathcal W(p)$ is convex for all $p\in Y$, then 
%
\[
\mathscr G(\mathcal W) = \{(p,z) \in\mathbb R^{d+n}: z\in\mathcal W(p)\}
\]
%
denotes the \emph{graph} of $\mathcal W$,
%
\begin{multline*}  
\text{int}(\mathscr G(\mathcal W)) = \{(p,z) \in\mathbb R^{d+n} : \exists \epsilon>0, \, z+\epsilon \zeta\in \mathcal W(p) \\ \forall \zeta\in\mathbb R^n\}
\end{multline*}
%
is its \emph{interior}, and
%
\[
  \partial \mathscr G(\mathcal W) = \mathscr G(\mathcal W)\setminus \textup{int}(\mathscr G(\mathcal W))
\]
%
denotes its \emph{boundary};
%
furthermore for any $(p,z)\in\partial\mathscr G(\mathcal W)$ the \emph{orientation cone} is defined as 
%
\[
  \mathcal N\mathcal W(p,z) = \{\zeta \in\mathbb R^n: z+\epsilon \zeta \not\in \mathcal W(p)\; \forall \epsilon>0\} .
\]
%for all $(p,x)\in\partial\mathscr G(\mathcal W)$.

\end{defi}
%
\begin{rem}
%
Note that the orientation cone is defined in the space of the
\emph{set variable} $z$ rather than \emph{graph variable} $(p,z)$.
%
Furthermore, the orientation cone contains all directions that 
point out of the set $\mathcal W(p)$ and hence all linear combinations thereof.
%
\end{rem}
%
The central idea connecting parametric convexity of a set valued map $\mathcal W$ with properties of its graph $\mathscr G(\mathcal W)$ is stated next.
%
\begin{thm}\label{thm:p:convexity:graph}
The map $\mathcal W$ is parametrically convex iff for all $(p_1,z_1), (p_2,z_2)\in\partial\mathscr G(\mathcal W)$
with $p_1\neq p_2$ and $\mathcal N\mathcal W(p_1,z_1)\cap\mathcal N\mathcal W(p_2,z_2)\neq\emptyset$,
%
\begin{equation}\label{eq:graph:def:p:convexity}
\lambda (p_1,z_1) + (1-\lambda) (p_2,z_2) \not\in\textup{int} (\mathscr G(\mathcal W))
\end{equation}
%
holds for all $\lambda\in(0,1)$.
%
\end{thm}
%
\begin{proof}
%
Assume~\eqref{eq:graph:def:p:convexity} holds for $(p_1,z_1),(p_2,z_2)\in\partial\mathscr G(\mathcal W)$.
%
Then the extension of the definition of the Minkowski functional (see e.g.~\cite{Rudin:91}) to the graph $\mathscr G(\mathcal W)$,
\[
\mu_{\mathscr G(\mathcal W)} \bigl(
\mathcal W(p), z \bigr)
:= \min_\mu \{\mu \geq 0 : z \in \mu \mathcal W(p)\},
\]
yields $\mu_{\mathscr G(\mathcal W)}\left(\mathcal W(\lambda p_1 + (1-\lambda)p_2),\lambda z_1+(1-\lambda)z_2\right)\geq1$ for all $\lambda\in(0,1)$. Therefore $\lambda z_1 + (1-\lambda) z_2$
lies either outside the set $\mathcal W(\lambda p_1+(1-\lambda)p_2)$ or on its boundary for all $\lambda\in(0,1)$, and hence the set of all possible interpolation points 
%
\[
\begin{split}
  \lambda \mathcal W(p_1)\oplus (1-\lambda)\mathcal W(p_2) = \{&z : z=\lambda z_1 + (1-\lambda) z_2,\\ &z_1\in\mathcal  W(p_1),\, z_2\in\mathcal W(p_2)\}
\end{split}
\]
%
contains the set $\mathcal W(\lambda p_1 + (1-\lambda)p_2)$ for all $\lambda\in(0,1)$.
%

Now suppose that $\mathcal W$ is parametrically convex and that~\eqref{eq:graph:def:p:convexity} is not satisfied for 
some $(p_1,z_1),(p_2,z_2)\in\partial\mathscr G(\mathcal W)$ with $\mathcal N\mathcal W(p_1,z_1)\cap\mathcal 
N\mathcal W(p_2,z_2)\neq\emptyset$, 
%
i.e.~that there exists $\epsilon>0$ such that the ball
$B_\epsilon(\lambda z_1 + (1-\lambda)z_2 )$
is contained in $\mathcal W(\lambda p_1 + (1-\lambda)p_2)$ for some $\lambda \in (0,1)$.
%i.e. $B_\epsilon(\lambda z_1 + (1-\lambda)z_2 )\subset \mathcal W(\lambda p_1 + (1-\lambda)p_2)$ for some $\epsilon>0$.
%
But this implies that $\lambda z_1 + (1-\lambda) z_2 + \epsilon\zeta \in \mathcal W(\lambda p_1+(1-\lambda)p_2)$  for all $\zeta\in\mathbb R^n$ such that $\|\zeta\| = 1$, whereas
$\mathcal N\mathcal W(p_1,z_1)\cap\mathcal N\mathcal W(p_2,z_2)\neq\emptyset$ implies that there exists 
$\zeta \in\mathcal N\mathcal W(p_1,z_1)\cap\mathcal N\mathcal W(p_2,z_2)$ which cannot be represented as
$\zeta =\lambda \zeta_1+
(1-\lambda)\zeta_2$
with $z_1 + \epsilon \zeta_1\in\mathcal W(p_1)$ and $z_2  + \epsilon \zeta_2\in\mathcal W(p_2)$.
%however since $B_\epsilon$ is full dimensional
%all directions exist, $x+\epsilon \xi\in\mathcal W(\lambda p_1 + (1-\lambda)p_2)$.
%
It follows that $\mathcal W$ cannot be parametrically convex in this case.
\end{proof}
%

Condition~\eqref{eq:graph:def:p:convexity} requires that the graph $\mathscr G(\mathcal W)$ is non-convex.
%
Indeed it is shown next that if $\mathscr G(\mathcal W)$ is strictly convex at any $(p,z)\in\partial \mathscr G (\mathcal W)$, then~\eqref{eq:graph:def:p:convexity} is violated and 
$\mathcal W$ cannot be parametrically convex.

@@

Let $\mathcal W(p):=\{z\in\mathbb R^n: r(p,z)\leq0\}$ define a point-to-set
map where 

@@

then $\mathcal W$ is parametrically
convex iff the function $r$ is concave in $p\in\mathbb R^d$.

@@

First note that $r(p,z)$ is assumed to be a convex function of $z$ for any given value of $p$ so that $\mathcal W(p)$ is a convex set for each $p\in\mathbb R^d$.
Suppose that, for given $z\in\mathbb R^n$, $r(p,z)$ is a non-concave (i.e. 
strictly convex) function of $p$, for all $p$ in some region $\Omega\subseteq\mathbb R^d$. 
Then any convex subset $\mathcal C\subseteq\Omega$ will be such that $\mathscr 
G(\mathcal W)\vert_{\mathcal C}$ is a convex set.
Furthermore, for any $(p_1,z_1),(p_2,z_2)\in \partial\mathscr G(\mathcal W)\vert_{\mathcal C}$ we have
$\lambda (p_1,z_1) + (1-\lambda) (p_2,z_2) \in\mathrm{int} (\mathscr G(\mathcal W))\vert_{\mathcal C}$ for all $\lambda\in(0,1)$ since
$\mathscr G(\mathcal W)\vert_{\mathcal C}$ is strictly convex in $p$.
Hence~\eqref{eq:graph:def:p:convexity} is violated in this case, implying that $r(p,z)$ cannot be a non-concave function of $p$ in any non-empty set $\Omega$ if $\mathcal W$ is parametrically convex. 
Conversely, if $r(p,z)$ is concave in $p$ for all $p\in\mathbb R^d$, then the conditions of Theorem~\ref{thm:p:convexity:graph} necessarily hold.
%then~\eqref{eq:graph:def:p:convexity} necessarily holds.
\begin{cor}\label{thm:polytopic:set:not:p:convex}
The polytopic parametric set valued map $\mathcal W(p):=\{z: a_i z + b_i p\leq c_i \; \forall i\in\mathbb N_m\}$
%i\leq m\}$ 
is not parametrically convex for 
any non-zero matrix $B^T = [\begin{matrix} b_1^T & \cdots & b_m^T\end{matrix}]$.
If $B\neq 0$, then the graph
\begin{equation*}
	\mathscr G(\mathcal W) = \{(p,z):a_i z + b_i p\leq c_i \; \forall i\in\mathbb N_m\} ,
\end{equation*}
is convex and violates the conditions of Theorem~\ref{thm:p:convexity:graph}.

@@

  \mathcal W(p) := \Bigl\{z: a_i z \leq \max_{k}\{b_{i,k} + c_{i,k}p\} \; \forall i\in\mathbb N_m \Bigr\}

@@

For clarity this proof is divided in 3 parts:
\begin{enumerate}
\item Note that $h_i(p) = \max_{k} \{b_{i,k} + c_{i,k}p\}$ is a multi-parametric linear program (mpLP),
the solution of which is a piecewise affine function $h_i(p) = b_{i,k^\ast_i} + c_{i,k^\ast_i}p$, where $k^\ast_i(p)$ is piecewise constant on a polytopic complex (see e.g.~\cite{spjotvold:2005}).
This means that there exists a finite partition 
of $\mathbb R^d$ 
% = \bigcup_{j\leq t} \mathcal P_j$
into convex polyhedra 
$\mathcal P_j$ such that $\bigcup_{j\in\mathbb N_t} \mathcal P_j = \mathbb R^d$ and 
${\bf{k}}^\ast(p) = (k_1^\ast(p),\dots,k_m^\ast(p))$ is constant for all $p \in \mathcal P_j$.
% A standard degeneracy assumption is that in neighbouring partitions ${\bf{k}}^\ast\vert_{\mathcal P_{j_1}}$ and 
% ${\bf{k}}^\ast\vert_{\mathcal P_{j_2}}$ differ by exactly one element.
Hence the graph $\mathscr G(\mathcal W)$ is given by a finite union of polyhedra
\begin{equation*}
  \mathscr G(\mathcal W) = \bigcup_{j\in\mathbb N_t} \left\{z: a_i z \leq b_{i,k_i^\ast} + c_{i,k_i^\ast}p \; \forall i \in\mathbb N_m \right\}\bigr\vert_{\mathcal P_{j}}
\end{equation*}
and it follows that if the number of vertices or rays changes within any partition $\mathcal P_j$ then $\mathscr
G(\mathcal W)\vert_{\mathcal P_j}$ is a strictly convex polyhedron and Corollary~\ref{thm:polytopic:set:not:p:convex} applies.
\item Our attention is therefore concentrated on the boundaries of partitions $\mathcal P_j$, at points $p\in\mathcal P_{j_1} \cap \mathcal P_{j_2}$ where 
%some mpLP changes its solution, i.e. 
$\bigl(b_{i,k_i^\ast} + c_{i,k_{j_1}^\ast} p\bigr)\bigr\rvert_{\mathcal P_{j_1}} = 
\bigl(b_{i,k_{j_2}^\ast} + c_{i,k_{j_2}^\ast} p\bigr)\bigr\rvert_{\mathcal P_{j_2}}$.
Notice that a vertex $v_\kappa(p)$ is defined by \emph{active} and \emph{inactive} inequalities, namely $\mathcal A_\kappa(p)$ and
$\mathcal I_\kappa(p) = \mathbb N_m
%\{1,\dots,m\}
\setminus\mathcal A_\kappa(p)$ respectively, where
\begin{equation*}\begin{split}
  a_i v_\kappa(p) &= b_{i,k_i^\ast} + c_{i,k_i^\ast} p \quad\forall i\in\mathcal A_\kappa(p)\\
  a_i v_\kappa(p) &< b_{i,k_i^\ast} + c_{i,k_i^\ast} p \quad\forall i\in\mathcal I_\kappa(p) .
\end{split}\end{equation*}
A standard degeneracy assumption is that in neighbouring partitions ${\bf{k}}^\ast\vert_{\mathcal P_{j_1}}$
and ${\bf{k}}^\ast\vert_{\mathcal P_{j_2}}$ differ by exactly one element.
Hence, in order for the number of vertices to change, there must be a hyperplane $fp=g$, such that the number of vertices for $fp \leq g$ is 
$N$ and for $fp>g$ is at least $N+1$.
It follows from the previous discussion that $\{p:fp=g\} = \textup{aff}\{\mathcal P_{j_1}\cap\mathcal P_{j_2}\}$ for some $j_1\neq j_2$.
In order for vertices $v_{\kappa_1}(p)$ and $v_{\kappa_2}(p)$ to merge, the index sets $\mathcal A_{\kappa_1}(p)$ and 
$\mathcal A_{\kappa_2}(p)$ have to differ by only one 
element, i.e.\ $\mathcal A_{\kappa_1}(p) = \mathcal J\cup \{s\}$ and $\mathcal A_{\kappa_2}(p) = \mathcal J\cup\{u\}$ if $fp>g$.
Furthermore, for $p$ such that $fp\leq g$ we have $v_{\kappa_1}(p)=v_{\kappa_2}(p)$, implying that $\mathcal A_{\kappa_1}(p) = 
\mathcal A_{\kappa_2}(p)$.
Since only one change in the active index set is considered (due to non-degeneracy assumptions), we must have
$\mathcal A_{\kappa_1}(p) = \mathcal A_{\kappa_2}(p) = \mathcal J \cup \{s,u\}$.
Hence on the hyperplane $fp=g$, both the maximising index ${\bf{k}}^\ast(p)$ and the active index sets $\mathcal A_{\kappa_1}(p)$ 
and $\mathcal A_{\kappa_2}(p)$ must change, which implies that the problem is degenerate.
\item In order for a degenerate graph $\mathscr G(\mathcal W)$ to be parametrically convex, the vertices $v_{\kappa_1}(p)$ and $v_{\kappa_2}(p)$ must be identical for $fp\leq g$, and in particular their dependence on $p$ has to be identical.
This can be expressed using the implicit function theorem as follows
\begin{align*}
  \frac{d}{dp}\left(  {\bf{a}}_{\mathcal J\cup \{s\}} v_{\kappa_1}(p) - {\bf{b}}_{\mathcal J\cup \{s\}} - 
  {\bf{c}}_{\mathcal J\cup \{s\},{\bf{k}}^\ast} p\right) &= 0\\
  \frac{d}{dp}\left(  {\bf{a}}_{\mathcal J\cup \{u\}} v_{\kappa_2}(p) - {\bf{b}}_{\mathcal J\cup \{u\}} - 
  {\bf{c}}_{\mathcal J\cup \{u\},{\bf{k}}^\ast} p\right) &= 0
\end{align*}
implies
\begin{align*}
  {\bf{a}}_{\mathcal J\cup \{s\}} \frac{dv_{\kappa}}{dp} &= {\bf{c}}_{\mathcal J\cup \{s\},{\bf{k}}^\ast}\\
  {\bf{a}}_{\mathcal J\cup \{u\}} \frac{dv_{\kappa}}{dp} &= {\bf{c}}_{\mathcal J\cup \{u\},{\bf{k}}^\ast}
\end{align*}
and since we can assume that the inequalities are non-redundant for some right hand side, we find that 
\begin{equation}\label{eq:derivative:condition:on:index:sets}
  \frac{dv_\kappa}{dp} = {\bf{a}}_{\mathcal J\cup \{s\}}^{-1}{\bf{c}}_{\mathcal J\cup \{s\},{\bf{k}}^\ast} = 
  {\bf{a}}_{\mathcal J\cup \{u\}}^{-1}{\bf{c}}_{\mathcal J\cup \{u\},{\bf{k}}^\ast}
has to hold for the degenerate graph to remain parametrically convex.
To complete the proof we note that~\eqref{eq:derivative:condition:on:index:sets} is a degenerate condition, in the sense that an arbitrarily small perturbation will result in $v_{\kappa_1}(p) \neq v_{\kappa_2}(p)$, and we therefore disregard this possibility.
\end{enumerate}
\vskip-1.15\baselineskip

>>>>

%% Ticket list
\openTickets{Manuel:convHull,Manuel:wlog,Manuel:invertability:assumption,Mark:log:bounds,Mark:proof:cor15,Manuel:generic}

@@

% In this section we define the property of \emph{parametric convexity} in the context of set valued maps (so called point-to-set maps, see e.g.~\cite{Hogan:1973}). This property is then used 
% %here and in Section~\ref{sec:example:I} 
% to demonstrate the convexity of a generalised Pontryagin difference and thus determine the conditions under which $\mathcal{X}^\infty$ and $\mathcal{X}_i$ are convex polyhedra. 
% In this section we refer to sets $Y\subseteq\mathbb R^d$ and $Z\subseteq\mathbb R^n$, and we denote the power set of $Z$ as $\mathscr P(Z)$.
In this section we define \emph{parametric convexity} and summarise relevant results together with the central ideas on particular set-valued maps.
For a detailed discussion on parametric convexity we refer to~\cite{Schaich:2016comb}.

@@

\subsection{Properties of Parametrically Convex Maps}\label{ssec:properties:of:p:convex:maps}
%
In the following we present an equivalent characterisation of parametric convexity based on the \emph{graph} of the set-valued map.
% We begin by introducing an equivalent characterisation of parametric convexity that provides an insight into the geometrical properties of 
% point-to-set maps satisfying~(\ref{eq:def:parametrically:convex}).
%Definition~\ref{def:parametric:convexity}. 
% This is based on a description of parametric convexity in terms of conditions on the graph of a point-to-set map.
%
\begin{defi}\label{def:graph:of:map}
Let $\mathcal W:Y\rightarrow \mathscr P(Z)$ be a continuous point-to-set map
such that $\mathcal W(p)$ is convex for all $p\in Y$, then 
%
\[
\mathscr G(\mathcal W) = \{(p,z) \in\mathbb R^{d+n}: z\in\mathcal W(p)\}
\]
%
denotes the \emph{graph} of $\mathcal W$,
%
\begin{multline*}  
\text{int}(\mathscr G(\mathcal W)) = \{(p,z) \in\mathbb R^{d+n} : \exists \epsilon>0, \, z+\epsilon \zeta\in \mathcal W(p) \\ \forall \zeta\in\mathbb R^n\}
\end{multline*}
%
is its \emph{interior}, and
%
\[
  \partial \mathscr G(\mathcal W) = \mathscr G(\mathcal W)\setminus \textup{int}(\mathscr G(\mathcal W))
\]
%
denotes its \emph{boundary};
%
furthermore for any $(p,z)\in\partial\mathscr G(\mathcal W)$ the \emph{orientation cone} is defined as 
%
\[
  \mathcal N\mathcal W(p,z) = \{\zeta \in\mathbb R^n: z+\epsilon \zeta \not\in \mathcal W(p)\; \forall \epsilon>0\} .
\]
%for all $(p,x)\in\partial\mathscr G(\mathcal W)$.

\end{defi}
%
\begin{rem}
%
Note that the orientation cone is defined in the space of the
\emph{set variable} $z$ rather than \emph{graph variable} $(p,z)$.
%
Furthermore, the orientation cone contains all directions that 
point out of the set $\mathcal W(p)$ and hence all linear combinations thereof.
%
\end{rem}
%
The central idea connecting parametric convexity of a set valued map $\mathcal W$ with properties of its graph $\mathscr G(\mathcal W)$ is stated next.
%
\begin{thm}\label{thm:p:convexity:graph}
The map $\mathcal W$ is parametrically convex iff for all $(p_1,z_1), (p_2,z_2)\in\partial\mathscr G(\mathcal W)$
with $p_1\neq p_2$ and $\mathcal N\mathcal W(p_1,z_1)\cap\mathcal N\mathcal W(p_2,z_2)\neq\emptyset$,
%
\begin{equation}\label{eq:graph:def:p:convexity}
\lambda (p_1,z_1) + (1-\lambda) (p_2,z_2) \not\in\textup{int} (\mathscr G(\mathcal W))
\end{equation}
%
holds for all $\lambda\in(0,1)$.
%
\end{thm}
%
% \begin{proof} See~\cite{Schaich:2016comb}.
% %
% Assume~\eqref{eq:graph:def:p:convexity} holds for $(p_1,z_1),(p_2,z_2)\in\partial\mathscr G(\mathcal W)$.
% %
% Then the extension of the definition of the Minkowski functional (see e.g.~\cite{Rudin:91}) to the graph $\mathscr G(\mathcal W)$,
% \[
% \mu_{\mathscr G(\mathcal W)} \bigl(
% \mathcal W(p), z \bigr)
% := \min_\mu \{\mu \geq 0 : z \in \mu \mathcal W(p)\},
% \]
% yields $\mu_{\mathscr G(\mathcal W)}\left(\mathcal W(\lambda p_1 + (1-\lambda)p_2),\lambda z_1+(1-\lambda)z_2\right)\geq1$ for all $\lambda\in(0,1)$. Therefore $\lambda z_1 + (1-\lambda) z_2$
% lies either outside the set $\mathcal W(\lambda p_1+(1-\lambda)p_2)$ or on its boundary for all $\lambda\in(0,1)$, and hence the set of all possible interpolation points 
% %
% \[
% \begin{split}
%   \lambda \mathcal W(p_1)\oplus (1-\lambda)\mathcal W(p_2) = \{&z : z=\lambda z_1 + (1-\lambda) z_2,\\ &z_1\in\mathcal  W(p_1),\, z_2\in\mathcal W(p_2)\}
% \end{split}
% \]
% %
% contains the set $\mathcal W(\lambda p_1 + (1-\lambda)p_2)$ for all $\lambda\in(0,1)$.
% %

% Now suppose that $\mathcal W$ is parametrically convex and that~\eqref{eq:graph:def:p:convexity} is not satisfied for 
% some $(p_1,z_1),(p_2,z_2)\in\partial\mathscr G(\mathcal W)$ with $\mathcal N\mathcal W(p_1,z_1)\cap\mathcal 
% N\mathcal W(p_2,z_2)\neq\emptyset$, 
% %
% i.e.~that there exists $\epsilon>0$ such that the ball
% $B_\epsilon(\lambda z_1 + (1-\lambda)z_2 )$
% is contained in $\mathcal W(\lambda p_1 + (1-\lambda)p_2)$ for some $\lambda \in (0,1)$.
% %i.e. $B_\epsilon(\lambda z_1 + (1-\lambda)z_2 )\subset \mathcal W(\lambda p_1 + (1-\lambda)p_2)$ for some $\epsilon>0$.
% %
% But this implies that $\lambda z_1 + (1-\lambda) z_2 + \epsilon\zeta \in \mathcal W(\lambda p_1+(1-\lambda)p_2)$  for all $\zeta\in\mathbb R^n$ such that $\|\zeta\| = 1$, whereas
% $\mathcal N\mathcal W(p_1,z_1)\cap\mathcal N\mathcal W(p_2,z_2)\neq\emptyset$ implies that there exists 
% $\zeta \in\mathcal N\mathcal W(p_1,z_1)\cap\mathcal N\mathcal W(p_2,z_2)$ which cannot be represented as
% $\zeta =\lambda \zeta_1+
% (1-\lambda)\zeta_2$
% with $z_1 + \epsilon \zeta_1\in\mathcal W(p_1)$ and $z_2  + \epsilon \zeta_2\in\mathcal W(p_2)$.
% %however since $B_\epsilon$ is full dimensional
% %all directions exist, $x+\epsilon \xi\in\mathcal W(\lambda p_1 + (1-\lambda)p_2)$.
% %
% It follows that $\mathcal W$ cannot be parametrically convex in this case.
% \end{proof}
%

Condition~\eqref{eq:graph:def:p:convexity} requires that the graph $\mathscr G(\mathcal W)$ is non-convex in the parameter~$p\in Y$.
%
% Indeed it is shown next that if $\mathscr G(\mathcal W)$ is strictly convex at any $(p,z)\in\partial \mathscr G (\mathcal W)$, then~\eqref{eq:graph:def:p:convexity} is violated and 
% $\mathcal W$ cannot be parametrically convex.
%
The next statement makes~\eqref{eq:graph:def:p:convexity} more precise.

@@

Let $\mathcal W(p):=\{z\in\mathbb R^n: r(p,z)\leq0\}$ define a set-valued map where 

@@

then $\mathcal W$ is parametrically convex iff the function $r$ is concave in $p\in\mathbb R^d$.

@@

% \begin{proof}
% First note that $r(p,z)$ is assumed to be a convex function of $z$ for any given value of $p$ so that $\mathcal W(p)$ is a convex set for each $p\in\mathbb R^d$.
% Suppose that, for given $z\in\mathbb R^n$, $r(p,z)$ is a non-concave (i.e. 
% strictly convex) function of $p$, for all $p$ in some region $\Omega\subseteq\mathbb R^d$. 
% Then any convex subset $\mathcal C\subseteq\Omega$ will be such that $\mathscr 
% G(\mathcal W)\vert_{\mathcal C}$ is a convex set.
% Furthermore, for any $(p_1,z_1),(p_2,z_2)\in \partial\mathscr G(\mathcal W)\vert_{\mathcal C}$ we have
% $\lambda (p_1,z_1) + (1-\lambda) (p_2,z_2) \in\mathrm{int} (\mathscr G(\mathcal W))\vert_{\mathcal C}$ for all $\lambda\in(0,1)$ since
% $\mathscr G(\mathcal W)\vert_{\mathcal C}$ is strictly convex in $p$.
% Hence~\eqref{eq:graph:def:p:convexity} is violated in this case, implying that $r(p,z)$ cannot be a non-concave function of $p$ in any non-empty set $\Omega$ if $\mathcal W$ is parametrically convex. 
% Conversely, if $r(p,z)$ is concave in $p$ for all $p\in\mathbb R^d$, then the conditions of Theorem~\ref{thm:p:convexity:graph} necessarily hold.
% %then~\eqref{eq:graph:def:p:convexity} necessarily holds.
% \end{proof}
% \begin{cor}\label{thm:polytopic:set:not:p:convex}
% The polytopic parametric set valued map $\mathcal W(p):=\{z: a_i z + b_i p\leq c_i \; \forall i\in\mathbb N_m\}$
% %i\leq m\}$ 
% is not parametrically convex for 
% any non-zero matrix $B^T = [\begin{matrix} b_1^T & \cdots & b_m^T\end{matrix}]$.
% \end{cor}
% \begin{proof}
% If $B\neq 0$, then the graph
% \begin{equation*}
% 	\mathscr G(\mathcal W) = \{(p,z):a_i z + b_i p\leq c_i \; \forall i\in\mathbb N_m\} ,
% \end{equation*}
% is convex and violates the conditions of Theorem~\ref{thm:p:convexity:graph}.
% \end{proof}

@@

  \mathcal W(p) := \Bigl\{z\in\mathbb R^n: a_i z \leq \max_{k}\{b_{i,k} + c_{i,k}p\} \; \forall i\in\mathbb N_m \Bigr\}

@@

% \begin{proof}
% For clarity this proof is divided in 3 parts:
% \begin{enumerate}
% \item Note that $h_i(p) = \max_{k} \{b_{i,k} + c_{i,k}p\}$ is a multi-parametric linear program (mpLP),
% the solution of which is a piecewise affine function $h_i(p) = b_{i,k^\ast_i} + c_{i,k^\ast_i}p$, where $k^\ast_i(p)$ is piecewise constant on a polytopic complex (see e.g.~\cite{spjotvold:2005}).
% This means that there exists a finite partition 
% of $\mathbb R^d$ 
% % = \bigcup_{j\leq t} \mathcal P_j$
% into convex polyhedra 
% $\mathcal P_j$ such that $\bigcup_{j\in\mathbb N_t} \mathcal P_j = \mathbb R^d$ and 
% ${\bf{k}}^\ast(p) = (k_1^\ast(p),\dots,k_m^\ast(p))$ is constant for all $p \in \mathcal P_j$.
% % A standard degeneracy assumption is that in neighbouring partitions ${\bf{k}}^\ast\vert_{\mathcal P_{j_1}}$ and 
% % ${\bf{k}}^\ast\vert_{\mathcal P_{j_2}}$ differ by exactly one element.
% Hence the graph $\mathscr G(\mathcal W)$ is given by a finite union of polyhedra
% \begin{equation*}
%   \mathscr G(\mathcal W) = \bigcup_{j\in\mathbb N_t} \left\{z: a_i z \leq b_{i,k_i^\ast} + c_{i,k_i^\ast}p \; \forall i \in\mathbb N_m \right\}\bigr\vert_{\mathcal P_{j}}
% \end{equation*}
% and it follows that if the number of vertices or rays changes within any partition $\mathcal P_j$ then $\mathscr
% G(\mathcal W)\vert_{\mathcal P_j}$ is a strictly convex polyhedron and Corollary~\ref{thm:polytopic:set:not:p:convex} applies.
% \item Our attention is therefore concentrated on the boundaries of partitions $\mathcal P_j$, at points $p\in\mathcal P_{j_1} \cap \mathcal P_{j_2}$ where 
% %some mpLP changes its solution, i.e. 
% $\bigl(b_{i,k_i^\ast} + c_{i,k_{j_1}^\ast} p\bigr)\bigr\rvert_{\mathcal P_{j_1}} = 
% \bigl(b_{i,k_{j_2}^\ast} + c_{i,k_{j_2}^\ast} p\bigr)\bigr\rvert_{\mathcal P_{j_2}}$.
% Notice that a vertex $v_\kappa(p)$ is defined by \emph{active} and \emph{inactive} inequalities, namely $\mathcal A_\kappa(p)$ and
% $\mathcal I_\kappa(p) = \mathbb N_m
% %\{1,\dots,m\}
% \setminus\mathcal A_\kappa(p)$ respectively, where
% \begin{equation*}\begin{split}
%   a_i v_\kappa(p) &= b_{i,k_i^\ast} + c_{i,k_i^\ast} p \quad\forall i\in\mathcal A_\kappa(p)\\
%   a_i v_\kappa(p) &< b_{i,k_i^\ast} + c_{i,k_i^\ast} p \quad\forall i\in\mathcal I_\kappa(p) .
% \end{split}\end{equation*}
% \todo{Manuel:generic}{Since $\mathcal W(p)$ is assumed to be generic, it has to be generic for every~$p\in\mathbb R^d$, which means it is \emph{simple}, i.e. each vertex is defined by exactly $n$ active inequalities $\abs{\mathcal A_\kappa(p)}=n$ for all $p\in\mathbb R^d$ and all $\kappa$.}
% Another standard degeneracy assumption is that in neighbouring partitions ${\bf{k}}^\ast\vert_{\mathcal P_{j_1}}$
% and ${\bf{k}}^\ast\vert_{\mathcal P_{j_2}}$ differ by exactly one element.
% Hence, in order for the number of vertices to change, there must be a hyperplane $fp=g$, such that the number of vertices for $fp \leq g$ is 
% $N$ and for $fp>g$ is at least $N+1$.
% It follows from the previous discussion that $\{p:fp=g\} = \textup{aff}\{\mathcal P_{j_1}\cap\mathcal P_{j_2}\}$ for some $j_1\neq j_2$.
% In order for vertices $v_{\kappa_1}(p)$ and $v_{\kappa_2}(p)$ to merge, the index sets $\mathcal A_{\kappa_1}(p)$ and 
% $\mathcal A_{\kappa_2}(p)$ have to differ by only one 
% element, i.e.\ $\mathcal A_{\kappa_1}(p) = \mathcal J\cup \{s\}$ and $\mathcal A_{\kappa_2}(p) = \mathcal J\cup\{u\}$ if $fp>g$.
% Furthermore, for $p$ such that $fp\leq g$ we have $v_{\kappa_1}(p)=v_{\kappa_2}(p)$, implying that $\mathcal A_{\kappa_1}(p) = 
% \mathcal A_{\kappa_2}(p)$.
% Since only one change in the active index set is considered (due to non-degeneracy assumptions), we must have
% $\mathcal A_{\kappa_1}(p) = \mathcal A_{\kappa_2}(p) = \mathcal J \cup \{s,u\}$.
% Hence on the hyperplane $fp=g$, both the maximising index ${\bf{k}}^\ast(p)$ and the active index sets $\mathcal A_{\kappa_1}(p)$ 
% and $\mathcal A_{\kappa_2}(p)$ must change, which implies that the problem is degenerate.
% \item In order for a degenerate graph $\mathscr G(\mathcal W)$ to be parametrically convex, the vertices $v_{\kappa_1}(p)$ and $v_{\kappa_2}(p)$ must be identical for $fp\leq g$, and in particular their dependence on $p$ has to be identical.
% This can be expressed using the implicit function theorem as follows
% \begin{align*}
%   \frac{d}{dp}\left(  {\bf{a}}_{\mathcal J\cup \{s\}} v_{\kappa_1}(p) - {\bf{b}}_{\mathcal J\cup \{s\}} - 
%   {\bf{c}}_{\mathcal J\cup \{s\},{\bf{k}}^\ast} p\right) &= 0\\
%   \frac{d}{dp}\left(  {\bf{a}}_{\mathcal J\cup \{u\}} v_{\kappa_2}(p) - {\bf{b}}_{\mathcal J\cup \{u\}} - 
%   {\bf{c}}_{\mathcal J\cup \{u\},{\bf{k}}^\ast} p\right) &= 0
% \end{align*}
% implies
% \begin{align*}
%   {\bf{a}}_{\mathcal J\cup \{s\}} \frac{dv_{\kappa}}{dp} &= {\bf{c}}_{\mathcal J\cup \{s\},{\bf{k}}^\ast}\\
%   {\bf{a}}_{\mathcal J\cup \{u\}} \frac{dv_{\kappa}}{dp} &= {\bf{c}}_{\mathcal J\cup \{u\},{\bf{k}}^\ast}
% \end{align*}
% and since we can assume that the inequalities are non-redundant for some right hand side, we find that 
% \begin{equation}\label{eq:derivative:condition:on:index:sets}
%   \frac{dv_\kappa}{dp} = {\bf{a}}_{\mathcal J\cup \{s\}}^{-1}{\bf{c}}_{\mathcal J\cup \{s\},{\bf{k}}^\ast} = 
%   {\bf{a}}_{\mathcal J\cup \{u\}}^{-1}{\bf{c}}_{\mathcal J\cup \{u\},{\bf{k}}^\ast}
% \end{equation}
% has to hold for the degenerate graph to remain parametrically convex.
% To complete the proof we note that~\eqref{eq:derivative:condition:on:index:sets} is a degenerate condition, in the sense that an arbitrarily small perturbation will result in $v_{\kappa_1}(p) \neq v_{\kappa_2}(p)$, and we therefore disregard this possibility.
% \end{enumerate}
% \vskip-1.15\baselineskip
% \end{proof}
\begin{rem}
